---
title: "Intro to R with R Markdown"
output: html_document
---

```{r setup, include=FALSE}
# This defines the behavior of your code chunks in your R Markdown document.
#   echo: do you want the code that you ran to print in the output?
#   eval: do you want the code to be evaluated (i.e., treated like real code)?
#       - Here we set it to false because this document is just an example and I don't care whether the code actually runs. For a summary document we'd want to set it to true (or just leave it off; its default is TRUE). 
#       - We can also set the value to be TRUE for individual chunks.
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

# Overview
## Goals

# Intro to R
## R packages and libraries
**Packages** are bundles of code written to do (typically) specific sets of functions

- Some packages are automatically downloaded and loaded into your workspace when you install R
- Others you have to explicitly download
- Many packages are hosted on CRAN - this is the official "home" of peer-approved packages
  - These can be installed using the function `install.packages()`.

```{r}
install.packages("tidyverse")
```

## Basic R uses

- Use as calculator
```{r}
3 + 2
10^4
4*100
```

- Create variables and store information in them
```{r}
x <- 5
```

- Print information to console

```{r eval=TRUE}
# Notice I set eval = TRUE in this chunk because I want x <- 5 to get evaluated so that it will accurately print the output!

print("Hello!")
print(3*5)

x <- 5 
x # this prints the value of x!
```

## Variables in R

- Numeric variables contain and are treated as numbers
- String variables are treated as strings of text (also known as character variables)
- Variables don't just hold numbers and text - they can hold sets of numbers/text, lists of various kinds of information, and whole data sets!

### Naming variables
- Be descriptive
- Be consistent in your content
- Be consistent in your case (camelCase/snake_case/etc)


