---
title: "Manuscript"
subtitle: "Generated using RMarkdown"
author:
- Thea Knowles^1^, Thea Knowles' Alter Ego^2^
- ^1^Western University, ^2^University of Western Ontario
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::word_document2:
    fig_caption: yes
    md_extensions: +footnotes
    reference_docx: custom_reference.docx
    toc: yes
  word_document:
    fig_caption: yes
    md_extensions: +footnotes
    reference_docx: custom_reference.docx
    toc: yes
  html_document:
    toc: yes
csl: apa.csl
bibliography: starbucks_refs.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load required packages
library(knitr)
library(rmarkdown)
library(ggplot2)
```


# Introduction
Here is an introduction. This paper explores the relationship between calorie content, total fat, and sugars in specialty coffee beverages made by the Starbucks industry.

Starbucks recently introduced calorie counts on their menus, a marketing move reflecting consumer trends motivated in part by the recent findings of [@bleich2015]. Other research on this topic will be cited here in parentheses [@drewnowski2003; @malik2010]. @weaver2003 demonstrated the use of an inline citation here. 

# Methods
Here is a nifty equation that shows absolutely nothing except how to include an equation and cite it: 

<!-- COMMENTS! -->
<!-- The text enclosed in dollar signs $ $ will be treated as LaTex math (an equation), and will be formatted especially for this -->

<!-- Want to center text or an image that isn't in an R chunk? use <center> TEXT </center> -->

<center>
TEED = $\frac{10(coffee\ budget ^ 2)}{my\ income}* \$ 1\ bazillion$. 
</center>

The following table similarly demonstrates absolutely nothing useful except how to generate a simple table in RMarkdown.

|  Weekday  |  Kind of coffee I drank  | Happiness |
|:---------:|:------------------------:|:---------:|
|   Monday  |       Black coffee       |     5     |
|  Tuesday  |           Latte          |      4    |
| Wednesday |        Cappuccino        |     7     |
|  Thursday |       Black coffee       |     5     |
|   Friday  |         No coffee        |     0     |
|  Saturday |       Irish coffee       |     9     |
|   Sunday  | Orange mocha frappuccino |     11    |

# Results
<!-- This is a comment in RMarkdown main body text. Note how it differs from comments in R code (#). 
I have written the results section separately to keep things nice and tidy, and this is where I will call it as "child" input. 
It is important that R chunks (identifiable as sandwiched between three back ticks ```) in the child file don't have the same names as chunks in the main file. -->
```{r child = 'results.Rmd'}

```

# Discussion

# Limitations

# References

